\href{https://github.com/uds-datalab/PDBF}{PDBF} Documentation

### 2015-10-26 pdbf-doc.tex
small improvements in documentation, prepared new test to visually verify the integrity of procuced reference pdfs
part 1 of pdf and tar integration tests
pdf and tar integration tests finished. closing #2

integration tests now delete log and aux files after test

\section{Getting started}
\begin{itemize}
\item Make sure you have a Java Runtime (version $>=$ 1.7) installed
\item \href{https://github.com/uds-datalab/PDBF/archive/gh-pages.zip}{Download the latest version}
\item Extract zip and change workingdir to extracted folder
\item Adjust config.cfg
\item Try to compile pdbf-doc.tex file with this command: java -jar pdbf.jar pdbf-doc.tex
\item Open pdbf-doc.html, this is the final output of the compilation process, if you rename it to ".pdf" it is also a valid pdf-document
\item Optionally you can attach the included vldb-Invaders.ova (Space invaders clone) or \href{https://github.com/uds-datalab/PDBF/releases/download/1.0.1/dsl.ova}{download the dsl.ova} (Damn small linux) VirtualBox image and attach it to the compiled PDBF file with this command: java -jar pdbf.jar --vm pdbf-doc.html vldb-Invaders.ova
\item You can play around with the minimal.tex file which contains a minimal example of PDBF usage
\item For further information take a look at the \href{http://uds-datalab.github.io/PDBF/}{documentation}
\end{itemize}

@@

\subsection{Compile LaTeX to single HTML file}
You can also use the PDBF compiler to compile your LaTeX files to a single HTML file.
To do so just run the compiler as on any other document (you dont need to include the pdbf package in your tex file):\\[3pt]
\texttt{java -jar pdbf.jar sometexfile.tex}\\[3pt]
The resulting HTML file is saved in the same folder with the same name but html ending.

@@

\section{Thanks to}
phantomJS (\url{https://github.com/ariya/phantomjs})\\
Apache Commons IO (\url{http://commons.apache.org/proper/commons-io/})\\
Apache Commons Codec (\url{http://commons.apache.org/proper/commons-codec/})\\
google-gson (\url{https://github.com/google/gson})\\
postgreSQL JDBC Driver (\url{https://jdbc.postgresql.org/})\\
MariaDB JDBC Driver (\url{https://mariadb.com/kb/en/mariadb/about-the-mariadb-java-client/})\\
AlaSQL (\url{https://github.com/agershun/alasql})\\
C3 (\url{https://github.com/masayuki0812/c3})\\
D3 (\url{https://github.com/mbostock/d3})\\
Codemirror (\url{https://github.com/codemirror/codemirror})\\
google-diff-match-patch (\url{https://code.google.com/p/google-diff-match-patch/})\\
explorercanvas (\url{https://code.google.com/p/explorercanvas/})\\
DataTables (\url{https://github.com/DataTables/DataTables})\\
jQuery (\url{https://github.com/jquery/jquery})\\
jQuery-UI (\url{https://github.com/jquery/jquery-ui})\\
jStat (\url{https://github.com/jstat/jstat})\\
pivottable (\url{https://github.com/nicolaskruchten/pivottable})\\
PDF.js (\url{https://github.com/mozilla/pdf.js})\\
google-closure-compiler (\url{https://github.com/google/closure-compiler})\\
lz-string (\url{https://github.com/pieroxy/lz-string})\\

@@

\section{How to use the PDBF compiler}
Right now there are only two modes: \\[4pt]
-- The standart mode which compiles a tex file into the janiform PDBF format:\\
\verb|java -jar PDBF.jar LaTeX_file| \\[2pt]
-- The VM mode which attaches a VirtualBox .ova file to an existing PDBF:\\
\verb|java -jar PDBF.jar --vm PDBF_File.html VM_File.ova|

@@

\noindent We extended AlaSQL with the following statistical sql functions:\\[5pt]
\verb|GRUBBS_FILTER(arr, alpha, max)|: \\
\indent Desc.: Filters an array of values with a two-sided \href{http://en.wikipedia.org/wiki/Grubbs'_test_for_outliers}{grubbs test}. The grubbs test is performed on the whole array. If a significant outlier is detected (Z > ZCrit) and the relative margin of error is not too high (margin\_of\_error / avg > 0.025) then the outlier is removed. This procedure is repeated until one of these two conditions fails.\\
\indent Returns the filtered array.\\[3pt]
\indent \option
{arr}
{Array on which the operation is performed.}
{JavaScript array}
{No default value. Value must always be set!}
\indent \option
{alpha}
{significance level}
{Number $>$ 0 AND Number $<$ 1}
{\texttt{0.05}}\\[3pt]
%
\verb|MEAN(arr)|: \\
\indent Desc.: Calculates the \href{http://en.wikipedia.org/wiki/Arithmetic_mean}{arithmetic mean} of an array of values.\\
\indent Returns the arithmetic mean of the array.\\[3pt]
\indent \option
{arr}
{Array on which the operation is performed.}
{JavaScript array}
{No default value. Value must always be set!}\\[3pt]
%
\verb|STDDEV_SAMP(arr)|: \\
\indent Desc.: Calculates the \href{http://en.wikipedia.org/wiki/Standard_deviation}{ sample standard deviation} of an array of values.\\
\indent Returns the sample standard deviation of the array.\\[3pt]
\indent \option
{arr}
{Array on which the operation is performed.}
{JavaScript array}
{No default value. Value must always be set!}\\[3pt]
%
\verb|MARGIN_OF_ERROR(arr, alpha)|: \\
\indent Desc.: Calculates the \href{http://en.wikipedia.org/wiki/Margin_of_error}{margin of error} of an array of values.\\
\indent Returns the margin of error of the array.\\[3pt]
\indent \option
{arr}
{Array on which the operation is performed.}
{JavaScript array}
{No default value. Value must always be set!}
\indent \option
{alpha}
{significance level}
{Number $>$ 0 AND Number $<$ 1}
{\texttt{0.05}}\\[3pt]
%
\verb|CONF_INT(arr, alpha)|: \\
\indent Desc.: Calculates the \href{http://en.wikipedia.org/wiki/Confidence_interval}{confidence interval} of an array.\\
\indent Returns the confidence interval of the array.\\[3pt]
\indent \option
{arr}
{Array on which the operation is performed.}
{JavaScript array}
{No default value. Value must always be set!}
\indent \option
{alpha}
{significance level}
{Number $>$ 0 AND Number $<$ 1}
{\texttt{0.05}}\\[3pt]
%
\verb|T_TEST(arr1, arr2, alpha)|: \\
\indent Desc.: Performs a \href{http://en.wikipedia.org/wiki/Student's_t-test}{Student's t-test} on two arrays.\\
\indent Returns true if they are indistinguishable, and returns false otherwise.\\[3pt]
\indent \option
{arr1, arr2}
{Arrays on which the operation is performed.}
{JavaScript array}
{No default value. Value must always be set!}
\indent \option
{alpha}
{significance level}
{Number $>$ 0 AND Number $<$ 1}
{\texttt{0.05}}\\[3pt]
%
\verb|WELCH_TEST(arr1, arr2, alpha)|:\\
\indent Desc.: Performs a \href{http://en.wikipedia.org/wiki/Welch's_t_test}{Welch's t-test} on two arrays.\\
\indent Returns true if they are indistinguishable, and returns false otherwise.\\[3pt]
\indent \option
{arr1, arr2}
{Arrays on which the operation is performed.}
{JavaScript array}
{No default value. Value must always be set!}
\indent \option
{alpha}
{significance level}
{Number $>$ 0 AND Number $<$ 1}
{\texttt{0.05}}\\[3pt]
%
\section{Data sources}

@@

\section{PDBF elements}
\textbf{Note:} All PDBF elements use the font size, font family, and font style that was active at the point of their definition. You can for example surround all commands with \verb|\textbf{...}|, \verb|\emph{...}| or any other font command.\\[3pt]
\subsection{Chart}
\begin{figure}[h!]%
\hspace{-218pt}Examples:\\
    \centering
    \begin{minipage}{.48\textwidth}
    \chart[width=\textwidth, height=0.6\textwidth, chartType=line]{SELECT * FROM test;}
    \caption{Line Chart}
    \end{minipage}
    \hspace{11pt}
    \begin{minipage}{.48\textwidth}
    \chart[width=\textwidth, height=0.6\textwidth, chartType=bar]{SELECT * FROM test;}
    \caption{Bar Chart}
    \end{minipage} \\[8pt]
    \begin{minipage}{1.0\textwidth}
    \chart[width=\textwidth, height=0.36\textwidth, chartType=signatureplot]{SELECT b FROM test;}
    \caption{Signatureplot Chart}
    \end{minipage}
\end{figure}

\newpage
\noindent Macros: \\[3pt]
\verb|\chart[options][queryForOverlay]{queryForPage}| \\
\textbf{Note:} if \verb|queryForOverlay| is omitted the \verb|queryForPage| is used for the overlay.\\
\textbf{Note:} The first column of the query result is used for the x-Axis, all other columns are used for y-Axis.\\[8pt] 
\noindent Options:\\[3pt]
%
\option
{name}
{Sets the name of this element. This is only useful for linking Elements. See DataText.}
{String}
{\texttt{undefined}}

>>>>

\section{Getting started}
\begin{itemize}
\item Make sure you have a Java Runtime (version $>=$ 1.7) installed
\item \href{https://github.com/uds-datalab/PDBF/archive/gh-pages.zip}{Download the latest version}
\item Extract zip and change workingdir to extracted folder
\item Adjust config.cfg
\item Try to compile pdbf-doc.tex file with this command: \texttt{java -jar pdbf.jar pdbf-doc.tex}
\item Open pdbf-doc.html, this is the final output of the compilation process, if you rename it to ".pdf" it is also a valid pdf-document
\item Optionally you can attach the included vldb-Invaders.ova (Space invaders clone) or \href{https://github.com/uds-datalab/PDBF/releases/download/1.0.1/dsl.ova}{download the dsl.ova} (Damn small linux) VirtualBox image and attach it to the compiled PDBF file with this command: \texttt{java -jar pdbf.jar --vm pdbf-doc.html vldb-Invaders.ova}.
\item Open pdbf-doc.ova, this is the final output with the attached ova file. Its still a valid pdf and html at the same time.
\item You can play around with the minimal.tex file which contains a minimal example of PDBF usage
\item For further information take a look at the \href{http://uds-datalab.github.io/PDBF/}{documentation}
\end{itemize}

@@

\subsection{Compile LaTeX to single HTML file}
You can also use the PDBF compiler to compile your LaTeX files to a single HTML file.
To do so just run the compiler as on any other document (you dont need to include the pdbf package in your tex file):\\[3pt]
\texttt{java -jar pdbf.jar sometexfile.tex}\\[3pt]
The resulting HTML file is saved in the same folder with the same name but with ".html" filename extension.

@@

\section{Thanks to}
phantomJS (\url{https://github.com/ariya/phantomjs})\\
Apache Commons (\url{http://commons.apache.org/})\\
Apache PDFBox (\url{https://pdfbox.apache.org/})\\
jTar (\url{https://github.com/kamranzafar/jtar})\\
google-gson (\url{https://github.com/google/gson})\\
postgreSQL JDBC Driver (\url{https://jdbc.postgresql.org/})\\
MariaDB JDBC Driver (\url{https://mariadb.com/kb/en/mariadb/about-the-mariadb-java-client/})\\
AlaSQL (\url{https://github.com/agershun/alasql})\\
C3 (\url{https://github.com/masayuki0812/c3})\\
D3 (\url{https://github.com/mbostock/d3})\\
Codemirror (\url{https://github.com/codemirror/codemirror})\\
google-diff-match-patch (\url{https://code.google.com/p/google-diff-match-patch/})\\
explorercanvas (\url{https://code.google.com/p/explorercanvas/})\\
DataTables (\url{https://github.com/DataTables/DataTables})\\
jQuery (\url{https://github.com/jquery/jquery})\\
jQuery-UI (\url{https://github.com/jquery/jquery-ui})\\
jStat (\url{https://github.com/jstat/jstat})\\
pivottable (\url{https://github.com/nicolaskruchten/pivottable})\\
PDF.js (\url{https://github.com/mozilla/pdf.js})\\
google-closure-compiler (\url{https://github.com/google/closure-compiler})\\
lz-string (\url{https://github.com/pieroxy/lz-string})\\

@@

\section{How to use the PDBF compiler}
Right now there are only two modes: \\[4pt]
-- The standart mode which compiles a tex file into the janiform PDBF format:\\
\verb|java -jar PDBF.jar LaTeX_file| \\[2pt]
\textbf{Note:} The compiled document can be found in the same folder as the tex file and has the same name as the tex file but ".html" filename extension.\\[8pt]
-- The VM mode which attaches a VirtualBox .ova file to an existing PDBF:\\
\verb|java -jar PDBF.jar --vm PDBF_File.html VM_File.ova|\\[2pt]
\textbf{Note:} The compiled document can be found in the same folder as the html file and has the same name as the html file but ".ova" filename extension.

@@

\noindent We extended AlaSQL with the following statistical sql functions:\\[5pt]
\verb|GRUBBS_FILTER(arr, alpha, max)|: \\
\indent Desc.: Filters an array of values with a two-sided \href{http://en.wikipedia.org/wiki/Grubbs'_test_for_outliers}{grubbs test}. The grubbs test is performed on the whole array. If a significant outlier is detected (Z > ZCrit) and the relative margin of error is not too high (margin\_of\_error / avg > 0.025) then the outlier is removed. This procedure is repeated until one of these two conditions fails.\\
\indent Returns the filtered array.\\[3pt]
\indent \option
{arr}
{Array on which the operation is performed.}
{JavaScript array}
{No default value. Value must always be set!}
\indent \option
{alpha}
{significance level}
{Number $>$ 0 AND Number $<$ 1}
{\texttt{0.05}}\\[3pt]
%
\verb|MEAN(arr)|: \\
\indent Desc.: Calculates the \href{http://en.wikipedia.org/wiki/Arithmetic_mean}{arithmetic mean} of an array of values.\\
\indent Returns the arithmetic mean of the array.\\[3pt]
\indent \option
{arr}
{Array on which the operation is performed.}
{JavaScript array}
{No default value. Value must always be set!}\\[3pt]
%
\verb|STDDEV_SAMP(arr)|: \\
\indent Desc.: Calculates the \href{http://en.wikipedia.org/wiki/Standard_deviation}{ sample standard deviation} of an array of values.\\
\indent Returns the sample standard deviation of the array.\\[3pt]
\indent \option
{arr}
{Array on which the operation is performed.}
{JavaScript array}
{No default value. Value must always be set!}\\[3pt]
%
\verb|MARGIN_OF_ERROR(arr, alpha)|: \\
\indent Desc.: Calculates the \href{http://en.wikipedia.org/wiki/Margin_of_error}{margin of error} of an array of values.\\
\indent Returns the margin of error of the array.\\[3pt]
\indent \option
{arr}
{Array on which the operation is performed.}
{JavaScript array}
{No default value. Value must always be set!}
\indent \option
{alpha}
{significance level}
{Number $>$ 0 AND Number $<$ 1}
{\texttt{0.05}}\\[3pt]
%
\verb|CONF_INT(arr, alpha)|: \\
\indent Desc.: Calculates the \href{http://en.wikipedia.org/wiki/Confidence_interval}{confidence interval} of an array.\\
\indent Returns the confidence interval of the array.\\[3pt]
\indent \option
{arr}
{Array on which the operation is performed.}
{JavaScript array}
{No default value. Value must always be set!}
\indent \option
{alpha}
{significance level}
{Number $>$ 0 AND Number $<$ 1}
{\texttt{0.05}}\\[3pt]
%
\verb|T_TEST(arr1, arr2, alpha)|: \\
\indent Desc.: Performs a \href{http://en.wikipedia.org/wiki/Student's_t-test}{Student's t-test} on two arrays.\\
\indent Returns true if they are indistinguishable, and returns false otherwise.\\[3pt]
\indent \option
{arr1, arr2}
{Arrays on which the operation is performed.}
{JavaScript array}
{No default value. Value must always be set!}
\indent \option
{alpha}
{significance level}
{Number $>$ 0 AND Number $<$ 1}
{\texttt{0.05}}\\[3pt]
%
\verb|WELCH_TEST(arr1, arr2, alpha)|:\\
\indent Desc.: Performs a \href{http://en.wikipedia.org/wiki/Welch's_t_test}{Welch's t-test} on two arrays.\\
\indent Returns true if they are indistinguishable, and returns false otherwise.\\[3pt]
\indent \option
{arr1, arr2}
{Arrays on which the operation is performed.}
{JavaScript array}
{No default value. Value must always be set!}
\indent \option
{alpha}
{significance level}
{Number $>$ 0 AND Number $<$ 1}
{\texttt{0.05}}\\[3pt]
%
\newpage
\section{Data sources}

@@

\newpage
\section{PDBF elements}
\textbf{Note:} All PDBF elements use the font size, font family, and font style that was active at the point of their definition. You can for example surround all commands with \verb|\textbf{...}|, \verb|\emph{...}| or any other font command.\\[3pt]
\subsection{Chart}
\begin{figure}[h!]%
\hspace{-218pt}Examples:\\
    \centering
    \begin{minipage}{.48\textwidth}
    \chart[width=\textwidth, height=0.6\textwidth, chartType=line]{SELECT * FROM test;}
    \caption{Line Chart}
    \end{minipage}
    \hspace{11pt}
    \begin{minipage}{.48\textwidth}
    \chart[width=\textwidth, height=0.6\textwidth, chartType=bar]{SELECT * FROM test;}
    \caption{Bar Chart}
    \end{minipage} \\[8pt]
    \begin{minipage}{1.0\textwidth}
    \chart[width=\textwidth, height=0.36\textwidth, chartType=signatureplot]{SELECT b FROM test;}
    \caption{Signatureplot Chart}
    \end{minipage}
\end{figure}

\noindent Macros: \\[3pt]
\verb|\chart[options][queryForOverlay]{queryForPage}| \\
\textbf{Note:} if \verb|queryForOverlay| is omitted the \verb|queryForPage| is used for the overlay.\\
\textbf{Note:} The first column of the query result is used for the x-Axis, all other columns are used for y-Axis.\\[8pt] 
\noindent Options:\\[3pt]
%
\option
{name}
{Sets the name of this element. This is only useful for linking Elements. See DataText.}
{String}
{\texttt{undefined}}
